Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-08-29 main.tex
Update on Overleaf.

@@

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
    \begin{align*}
        U := |\patch_{\calT}(S)| \setminus T.
    \end{align*}
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi : T \rightarrow U
    \end{align*}
    satisfying
    \begin{align*}
        \Lip( \Xi,      T ) \leq \Cvier{n}{k} \theta(\calT) \alpha(T)^{2},
        \quad 
        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k} \theta(\calT) \alpha(T)^{2},
    \end{align*}
    where $...$ and $\Cfive{n}{k} \leq ...$
    \begin{align*}
        \Cvier{n}{k} \leq 64 \left( \sqrt{n} + 1 \right) \Ceins{n} \Czwei{n}
        ,
        \qquad 
        \Cfive{n}{k} \leq 64 \left( \sqrt{n} + 1 \right) \Ceins{n} \Czwei{n}
    \end{align*}

    \todo{Complete the estimate.}
\end{theorem}
\begin{proof}
    We derive the estimate in several steps. 
    \begin{itemize}
        \item 
        Without loss of generality, the barycenter of $S$ is the origin. 
        % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        %We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        %So $J$ is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
        Note that $J$ is the union of exactly those faces of $T$ that contain $S'$.

@@

        in the following manner. Let $T \in \calR'$ be an $n$-dimensional simplex and let $x \in T$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.

@@

            \frac{ \| A_{T}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x

@@

            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{T}^{-1} x \|_{1} } x

@@

            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } x

@@

                ( A_{T}^{-t} \vecone \cdot y ) 

@@

                ( A_{T}^{-t} \vecone \cdot x )

@@

            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } y

@@

            \frac{ A_{T}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } 

@@

@@

            \frac{ \sigma_{\max}( A_{T}^{-1} ) }{ \sigma_{\min}( A_{K}^{-1} ) }

@@

            \frac{ \sigma_{\max}( A_{T}^{-1} ) \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{K}^{-2} ) }

@@

@@

            \frac{ \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{T}^{-1} ) }

@@

            \frac{ \sigma_{\max}( A_{K}^{-1} ) \sigma_{\max}( A_{T}^{-1} ) }{ \sigma_{\min}( A_{T}^{-2} ) }

@@

        is a mapping from $T$ onto $\overline{\patch_{\calT}(S) \setminus T}$.
        It preserves the interface from $T$ onto $U$. 

@@

        \item 
        We need to estimate the singular values of the transformation matrices within the bisected simplices. 
        Each bisection step reduces the diameter by at most a factor of one half,
        and it reduces the volume always by a factor of one half. 
        We use the estimates in Lemma~\ref{lemma:affinetransform}.
        This shows

        \color{red}
        \begin{align*}
            \| \Jacobian \Xi_{S} \| 
            &\leq 
            2 \left( \sqrt{n} + 1 \right) 
            \sup_{ K \in \calK  }
            \Ceins{n} \diam(K) 
            \sup_{ K \in \calR' } 
            \Czwei{n} \kappa(K) \diam(K)^{-1}
            \sup_{ K \in \calR  } \kappa(A_{K})
            \\&\leq 
            32 \left( \sqrt{n} + 1 \right) 
            \theta(\calT)
            \Ceins{n} 
            \Czwei{n} 
            \kappa(\calT) 
            \alpha(\calT)
            \\
            \| \Jacobian \Xi_{S}^{-1} \| 
            &\leq 
            2 \left( \sqrt{n} + 1 \right) 
            \sup_{ K \in \calK  }
            \Czwei{n} \kappa(K) \diam(K)^{-1}
            \sup_{ K \in \calR' } 
            \Ceins{n} \diam(K)
            \sup_{ K \in \calR  } \kappa(A_{K})
            \\
            &\leq 
            32 \left( \sqrt{n} + 1 \right) 
            \theta(\calT)
            \Ceins{n} 
            \Czwei{n} 
            \kappa(\calT) 
            \alpha(\calT)
            .
        \end{align*}
        Together with the definition of $\theta(\calT)$, the desired result follows.

    \end{itemize}
    The proof is complete. 
\end{proof}

\begin{remark}
    While the reflection mapping and its analysis in Theorem~\ref{theorem:starreflection} serve our purpose,
    it might be possible to improve the estimate with a different analysis or construction.
\end{remark}

>>>>

\usepackage{enumitem}
\setitemize[1]{left=0.0cm}

@@

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
    \begin{align*}
        U := |\patch_{\calT}(S)| \setminus T.
    \end{align*}
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi : T \rightarrow U
    \end{align*}
    satisfying
    \begin{align*}
        \Lip( \Xi,      T ) \leq \Cvier{n}{k}(\calT),
        \quad 
        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k}(\calT),
    \end{align*}
    where $\Cvier{n}{k}(\calT)$ and $\Cfive{n}{k}(\calT)$ are constants as stated in the proof. 
\end{theorem}
\begin{proof}
    We derive the estimate in several steps. 
    \begin{itemize}
        \item 
        Without loss of generality, the barycenter of $S$ is the origin. 
        % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        %We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        %So $J$ is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
        Note that $J$ is the union of exactly those faces of $T$ that contain $S'$.

@@

        in the following manner. Let ${G} \in \calR'$ be an $n$-dimensional simplex and let $x \in {G}$ be non-zero. There exists a simplex $K \in \calK$ that intersects the ray $\bbR_0^+ \cdot x$.

@@

            \frac{ \| A_{{G}}^{-1} x \|_{1} }{ \| A_{K}^{-1} x \|_{1} } x

@@

            \frac{ \| A_{K}^{-1} x \|_{1} }{ \| A_{{G}}^{-1} x \|_{1} } x

@@

            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } x

@@

                ( A_{{G}}^{-t} \vecone \cdot y ) 

@@

                ( A_{{G}}^{-t} \vecone \cdot x )

@@

            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot x } y

@@

            \frac{ A_{{G}}^{-t} \vecone \cdot x }{ A_{K}^{-t} \vecone \cdot  x } 

@@

        We see that the last summand is an oblique projection of $y$. 

@@

            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{K}^{-1} ) }

@@

            \frac{ \sigma_{\max}( A_{{G}}^{-1} ) \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{K}^{-2} ) }

@@

            \| \Jacobian \Psi^{-1}(x) \|

@@

            \frac{ \sigma_{\max}( A_{K}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-1} ) }

@@

            \frac{ \sigma_{\max}( A_{K}^{-1} ) \sigma_{\max}( A_{{G}}^{-1} ) }{ \sigma_{\min}( A_{{G}}^{-2} ) }

@@

        is a mapping from ${G}$ onto $U = \overline{\patch_{\calT}(S) \setminus {G}}$.
        It preserves the interface from ${G}$ onto $U$. 

@@

        \item 
        We need to estimate the singular values of the transformation matrices within the bisected simplices. 
        Each bisection step reduces the diameter by at most a factor of one half,
        and it reduces the volume always by a factor of one half. 
        We use the estimates in Lemma~\ref{lemma:affinetransform}.
        When $K \in \calK \cup \calS'r$, then 
        \begin{align*}
             \sigma_{\max}( A_{K}^{-1} )
             &\leq 
             \Czwei{n} \kappa(K) \diam(K)
             \leq 
             2 \Czwei{n} \kappa(\calT) \diam(K)^{-1}
             \\
             \sigma_{\min}( A_{K}^{-1} )^{-1}
             &= 
             \sigma_{\max}( A_{K} ) 
             \leq 
             \Ceins{n} \diam(K),
             \\ 
             \kappa( A_{K} )
             &\leq 
             \Csechs{n} \kappa(K) \leq 2 \Csechs{n} \kappa(\calT)
             .
        \end{align*}
        When ${G} \in \calR'$ is not our original simplex, then 
        \begin{align*}
             \sigma_{\max}( A_{{G}}^{-1} )
             &\leq 
             \Czwei{n} \kappa({G}) \diam({G})
             \leq 
             4 \Czwei{n} \kappa(\calT) \diam(G)^{-1},
             \\
             \sigma_{\min}( A_{{G}}^{-1} )^{-1}
             &= 
             \sigma_{\max}( A_{{G}} ) 
             \leq 
             \Ceins{n} \diam({G}),
             \\ 
             \kappa( A_{{G}} )
             &\leq 
             \Csechs{n} \kappa({G}) \leq 4 \Csechs{n} \kappa(\calT)
             .
        \end{align*}
        All the diameters above are comparable up to a factor of $\theta(\calT)$.
        In summary,
        \begin{gather*}
            \| \Jacobian \Theta_{|K}      \| \leq 2 \Csechs{n} \kappa(\calT)
            ,
            \qquad 
            \| \Jacobian \Theta_{|K}^{-1} \| \leq 2 \Csechs{n} \kappa(\calT)
            ,
            \\
            \| \Jacobian \Xi(x) \|
            \leq 
            \sqrt{n}
            4 
            \kappa(\calT) 
            \Ceins{n} 
            \Czwei{n} 
            \theta(\calT) % \frac{ \diam(K) }{ \diam(G) }
            \left( 
                1
                + 
                n
                2 \Csechs{n} \kappa(\calT)
                4 
                \kappa(\calT) 
                \Ceins{n} 
                \Czwei{n} 
                \theta(\calT) % \frac{ \diam(K) }{ \diam(G) }
            \right) 
            2 \Csechs{n} \kappa(\calT)
            ,
            \\
            \| \Jacobian \Xi^{-1}(x) \|
            \leq 
            \sqrt{n}
            2 
            \kappa(\calT) 
            \Ceins{n} 
            \Czwei{n} 
            \theta(\calT) % \frac{ \diam(G) }{ \diam(K) }
            \left( 
                1
                + 
                n
                2 \Csechs{n} \kappa(\calT)
                2 
                \kappa(\calT) 
                \Ceins{n} 
                \Czwei{n} 
                \theta(\calT) % \frac{ \diam(G) }{ \diam(K) }
            \right) 
            2 \Csechs{n} \kappa(\calT)
            .
        \end{gather*}
    \end{itemize}
    The proof is complete. 
\end{proof}

\begin{remark}
    While the reflection mapping and its analysis in Theorem~\ref{theorem:starreflection} serve our purpose,
    it might be possible to improve the estimate with an improved analysis or construction.
\end{remark}
